\section*{NeurIPS Paper Checklist}
\begin{enumerate}
\item {\bf Claims}
\item[] Question: Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
\item[] Answer: \answerYes{}.
\item[] Justification: The abstract and introduction state robust-training and conditional guarantees; these are supported in Sections 4--8.
\item {\bf Limitations}
\item[] Question: Does the paper discuss the limitations of the work performed by the authors?
\item[] Answer: \answerYes{}.
\item[] Justification: Section 9 discusses conditional guarantees, benchmark scope, and conservatism/runtime trade-offs.
\item {\bf Theory assumptions and proofs}
\item[] Question: For each theoretical result, does the paper provide the full set of assumptions and a complete (and correct) proof?
\item[] Answer: \answerYes{}.
\item[] Justification: Section 6 states assumptions and gives proof sketches for Propositions 1--4.
\item {\bf Experimental result reproducibility}
\item[] Question: Does the paper fully disclose all the information needed to reproduce the main experimental results of the paper to the extent that it affects the main claims and/or conclusions of the paper (regardless of whether the code and data are provided or not)?
\item[] Answer: \answerYes{}.
\item[] Justification: Sections 7--8 and Table 6 specify benchmark construction, metrics, and hyperparameters.
\item {\bf Open access to data and code}
\item[] Question: Does the paper provide open access to the data and code, with sufficient instructions to faithfully reproduce the main experimental results, as described in supplemental material?
\item[] Answer: \answerNo{}.
\item[] Justification: We provide detailed settings but no public code link in this submission artifact.
\end{enumerate}
